Multi-domain, multilingual translation with latent multi-task group dropout

### 2022-01-14 2022/acl/acl_latex.tex
8 pages version

\section{Conclusions and outlook}\label{sec:conclusion}
In this work, we have presented a novel method for multdomain and multilingual translation. It allows us to jointly search for an optimal assignment of sub-networks to tasks and to learn the parameters of the underlying network. Our method relies on a sound mathematical framework and an end-to-end optimization procedure which implies very little extra parameters. The training course is reasonably longer (100k iterations in multidomain translation) than training standard models while considering the gain in performance.\fyDone{There is a computational cost = 100k iterations} Experimentally, we achieve a large improvement over Transformer baseline without zero additional parameters; our performance are also comparable to that of a strong a multi-task baseline using residual adapter modules which however includes a large number of extra parameters. For multilingual translation, our model outperforms multilingual Transformer and Language Adapters in 3 our of 4 cases. Besides, we provided an thorough analysis of the similarities between learned sub-networks and demonstrated a strong correlation between the sub-networks' similarity and the proximity of the corresponding tasks (domain or language).

There are several ways in which our methodology could be improved and generalized. In future work, we would first like to provide an complete variational framework to model both the number of groups, $k$ and the selection of the dropout masks. Second, we also intend to get rid of the requirement of knowing the domain information during inference: this would mean replacing the dependency on $d$ in the variational distribution by a dependency in the input $x$. These two questions seem both very interesting and promising; they would allow to us to dispense with heuristic choices in the architecture, and replace them with an increase dependency on the training data.

>>>>

\section{Conclusions and outlook}\label{sec:conclusion}
In this work, we have presented a novel method for multdomain and multilingual translation. It allows us to jointly search for an optimal assignment of sub-networks to tasks and to learn the parameters of the underlying network. Our method relies on a sound mathematical framework and an end-to-end optimization procedure; it only adds a small number of extra parameters. The additional training cost is also reasonable, amounting to 100k iterations in the multidomain setting, given the observed gains in performance.\fyDone{There is a computational cost = 100k iterations} Experimentally, we achieve a large improvement over a Transformer baseline; our performance are also comparable to that of a strong a multi-task baseline using residual adapter modules which rely on a large number of extra parameters. For multilingual translation, our model outperforms multilingual Transformer and Language Adapters in 3 our of 4 settings. Besides, we provided an thorough analysis of the similarities between learned sub-networks and demonstrate a strong correlation between the learned similarities and the proximity of the corresponding tasks (domain or language).

There are several ways in which our methodology can be improved. In future work, we would first like to provide an complete variational framework to model both the number of groups, $k$ and the selection of the dropout masks. Second, we also intend to dispense with the domain information during inference: this would mean replacing the dependency on $d$ in the variational distribution by a dependency on the input $x$. Adressing these two questions will allow to us replace heuristic choices in the architecture design with an increased dependency on the training data.
